---
title: "raw data check&correct"
author: "Yixiao Chen"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# import packages
```{r}
library(tidyr)
library(dplyr)
library(stringr)
library(readr)
```

```{r}
# create an empty data frame to store the results
results <- data.frame(data_file = character(),
                      unique_ids = character(),
                      resCodeResult = character(),
                      score = character(),
                      stringsAsFactors = FALSE)
```

# For data 1833_DETECT_CallHistory_20220307.CSV
## import data
```{r}
additional_data <- read_csv("~/OneDrive-TheUniversityofTexasHealthScienceCenteratHouston (Archive)/DETECT/Preprocess MDAC Call Logs/data/1833_DETECT_CallHistory_20220307.CSV")
```

## check if any ID have scores after getting a completed code(69967, 0deb0)
```{r}
df1 <- additional_data %>%
  group_by(PTCARERPTNUM) %>%
  mutate(ResLastCallDate = ymd(ResLastCallDate)) %>%
  filter(ResLastCallDate < max(ResLastCallDate)) %>%
  filter(any(resCodeResult %in% c("CO", "97", "98"))) %>%
  select(PTCARERPTNUM,resCodeResult,ResLastCallDate)
```

## check if any ID with multiple scores but don't have a completed code (144e7)
```{r}
# get the IDs that have multiple scores but don't have a completed code
  data <- additional_data %>%
    group_by(PTCARERPTNUM) %>%
    mutate(non_miss_score = sum(!is.na(SCORE))) %>%
    filter(non_miss_score > 1) %>%
    summarise(unique_ids = paste0(PTCARERPTNUM),
              score = paste0(SCORE),
              resCodeResult = paste0(resCodeResult)) %>%
    mutate(data_file = "1833_DETECT_CallHistory_20220307.CSV")
  results <- bind_rows(results, data)
    
  
df2 <- results %>%
  group_by(PTCARERPTNUM) %>%
  filter(!any(resCodeResult %in% c("CO", "97", "98"))) %>%
  ungroup()
```

## manually check if those names have different ID 
### ALAN RICHARDS: 69967, 690f3(no score)
### LARRY HICKMAN: 0deb0, d3749(no score)
### Asa Eugene Pearson: 144e7

## Correct the records and generate new csv file
### manually correct 
```{r}
data <- read_csv("~/OneDrive-TheUniversityofTexasHealthScienceCenteratHouston (Archive)/DETECT/Preprocess MDAC Call Logs/data/1833_DETECT_CallHistory_20220307.CSV")
correct_data <- data %>%
  mutate(across(1:62, ~ ifelse(ResLastCallDate == 20220225 & MEDSTARID == "69967" | ResLastCallDate == 20220305 & MEDSTARID == "0deb0", NA, .))
         )
correct_data$OR_DATE[correct_data$PTCARERPTNUM == "1626da69bff94d918f6441c1a08144e7"] <- 20211207

```

### check the corrected data
```{r}
## check the correct data
rows_with_id_69967 <- correct_data %>%
  filter(MEDSTARID == "69967")
rows_with_id_69967

rows_with_id_0deb0 <- correct_data %>%
  filter(MEDSTARID == "0deb0"| MEDSTARID == "d3729")
rows_with_id_0deb0

rows_with_id_144e7 <- correct_data %>%
  filter(PTCARERPTNUM == "1626da69bff94d918f6441c1a08144e7")
rows_with_id_144e7
```

### export the corrected data
```{r}
write_csv(correct_data, "~/OneDrive-TheUniversityofTexasHealthScienceCenteratHouston (Archive)/DETECT/Preprocess MDAC Call Logs/data/correct_1833_DETECT_CallHistory_20220307.CSV")
```

# For other raw data
```{r}
# create a list of file names
data <- c("1833_DETECT_CallExport_20220524.CSV",
          "1833_DETECT_CallExport_20220613.CSV",
          "1833_DETECT_CallExport_20220623.CSV",
          "1833_DETECT_CallExport_20220713.CSV",
          "1833_DETECT_CallExport_20220726.CSV",
          "1833_DETECT_CallExport_20220808.CSV",
          "1833_DETECT_CallExport_20220825.CSV",
          "1833_DETECT_CallExport_20220912.CSV",
          "1833_DETECT_CallExport_20220922.CSV",
          "1833_DETECT_CallExport_20221011.CSV",
          "1833_DETECT_CallExport_20221024.CSV",
          "1833_DETECT_CallExport_20221109.CSV",
          "1833_DETECT_CallExport_20221123.CSV",
          "1833_DETECT_CallExport_20221209.CSV",
          "1833_DETECT_CallExport_20221223.CSV",
          "1833_DETECT_CallExport_20230110.CSV",
          "1833_DETECT_CallExport_20230125.CSV",
          "1833_DETECT_CallExport_20230210.CSV",
          "1833_DETECT_CallExport_20230222.CSV",
          "1833_DETECT_CallExport_20230310.CSV",
          "1833_DETECT_CallExport_20230324.CSV",
          "1833_DETECT_CallExport_20230410.CSV",
          "1833_DETECT_CallExport_20230424.CSV",
          "1833_DETECT_CallExport_20230510.CSV",
          "1833_DETECT_CallExport_20230522.CSV",
          "1833_DETECT_CallExport_20230522v2.CSV")
```

## check if any ID have scores after getting a completed code(no records have this issue)
```{r}
for (file_name in data) {
  call_history <- read_csv(paste0("~/UTHealth Houston/Cannell, Michael B - Outbound call logs/", file_name))
  
df1 <- call_history %>%
  group_by(PTCARERPTNUM) %>%
  mutate(ResLastCallDate = ymd(ResLastCallDate)) %>%
  filter(ResLastCallDate < max(ResLastCallDate)) %>%
  filter(any(resCodeResult %in% c("CO", "97", "98"))) %>%
  select(PTCARERPTNUM,resCodeResult,ResLastCallDate)

}
```

## check if any ID with multiple scores but don't have a completed code (6 records, see detailed in issue&reason.csv)
```{r}
for (file_name in data) {
  call_history <- read_csv(paste0("~/UTHealth Houston/Cannell, Michael B - Outbound call logs/", file_name))
  
  df <- call_history %>%
    group_by(PTCARERPTNUM) %>%
    mutate(non_miss_score = sum(!is.na(SCORE))) %>%
    filter(non_miss_score > 1) %>%
    summarise(unique_ids = paste0(PTCARERPTNUM),
              score = paste0(SCORE),
              resCodeResult = paste0(resCodeResult)) %>%
    mutate(data_file = file_name)
  
  results <- bind_rows(results, df)
}

# filter out PTCARERPTNUM with resCodeResult equal to CO, 97, or 98

results <- results %>%
  group_by(PTCARERPTNUM) %>%
  filter(!any(resCodeResult %in% c("CO", "97", "98"))) %>%
  ungroup()
```

## manually check if those names have different ID 
### for this 6 records, no participants have different MedstarID 

## Correct the records and generate new csv file
### manually correct
```{r}
data <- read.csv("~/UTHealth Houston/Cannell, Michael B - Outbound call logs/1833_DETECT_CallExport_20220922.CSV")
```

### check the corrected data
```{r}
data1 <- data
data1$resCodeResult[data$MEDSTARID == "ef204" & data$resCodeResult == 71] <- 97
```

### export the corrected data
```{r}
# Save the data as a CSV file
write.csv(data1, file = "~/UTHealth Houston/Cannell, Michael B - Outbound call logs/correct_1833_DETECT_CallExport_20220922.CSV", row.names = FALSE)
```